### 2016-09-25 results.tex
comments on Jon's meta-theorem, and instructions added to DS privacy result on how to handle in light of Jon's result
starting to generalize canonical representation def to multiple PRF keys

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \calK$.
\item $\pubaux \getsr \Rep_2(n, F_K(s_1), \ldots,F_K(s_t))$. 
\end{enumerate}
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}
\tsnote{Would be good to give an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. It does not cover
  linear-PRF or Neidermayer. }
We next show that any canonical data structure in which $F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

>>>>

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$;
\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1), \ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
\end{enumerate}
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}
\tsnote{Would be good to give an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover
  linear-PRF or Neidermayer. }
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
